Listed beneath are publications generated in relation to the research described in this thesis. These publications were accepted to conferences that adopted a peer review process.

\begin{enumerate}

%VRST
	\item Davies, C., Miller, A., and Allison, C. (2014). A View from the Hill: Where Cross Reality Meets Virtual Worlds.  Proceedings of the 20th ACM Symposium on Virtual Reality Software and Technology.

%Digital Heritage Marseille
	\item Davies, C., Miller, A., and Allison, C. (2013). Mobile Cross Reality for Cultural Heritage. Proceedings of the 2013 Digital Heritage International Congress (DigitalHeritage) federating the 19th Int'I VSMM, 10th Eurographics GCH, and 2nd UNESCO Memory of the World Conferences, plus special sessions from CAA, Arqueologica 2.0, Space2Place, ICOMOS ICIP and CIPA, EU projects, et al.

%iED Boston
	\item Davies, C., Allison, C., and Miller, A. (2013). PolySocial Reality for Education: Addressing the Vacancy Problem with Mobile Cross Reality. Proceedings of the 8th Immersive Education Summit.

%iED Boston
	\item Allison, C., Oliver, I., Miller, A., Davies, C. and McCaffery, J. (2013). From Metaverse to MOOC: Can the Cloud meet Scalability Challenges for Open Virtual Worlds? Proceedings of the 8th Immersive Education Summit.

%AINA
	\item Oliver, I., Miller, A., Allison, C., Dow, L., Campbell, A., Davies, C., and McCaffery, J. (2013). Towards the 3D Web with Open Simulator. Proceedings of the 27th IEEE International Conference on Advanced Information Networking and Applications.

%iED Europe
	\item Kennedy, S., Dow, L., Oliver, I., Sweetman, R., Miller, A., Campbell, A., Davies, C., McCaffery, J., Allison, C., Green, D., Luxford, J. and Fawcett, R. (2012). Living history with Open Virtual Worlds: Reconstructing St Andrews Cathedral as a stage for historic narrative. Proceedings of the 2nd European Immersive Education Summit.

%iED Europe
	\item Allison, C., Campbell, A., Davies, C., Dow, L., Kennedy, S., Miller, A., Oliver, I. and Perera, I. (2012). Growing the Use of Virtual Worlds in Education: an OpenSim Perspective. Proceedings of the 2nd European Immersive Education Summit.

%PGNet
	\item Davies, C., Miller, A., and Allison, C. (2012). Virtual Time Windows: Applying Cross Reality to Cultural Heritage. Proceedings of the 13th Annual Post Graduate Symposium on the Convergence of Telecommunications, Networking and Broadcasting.

\end{enumerate}